Insurance choice, decision assistance, and insurer steering

### 2021-05-03 finals/creed/creed-202105.Rmd
update presentations and filenames

---
title: "Insurance choice, decision assistance, and insurer steering"
subtitle: "Ian McCarthy & Evan Saltzman"
author: Emory University, Lunch and Learn
date: March 29, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
header-includes: 
  - \usepackage{graphicx}
  - \usepackage{amsmath}
output:
#  html_document: default (toggle on for "simplified" view)
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: ["macros.js","https://platform.twitter.com/widgets.js"]
#knit: pagedown::chrome_print
---

@@

.center[
  ![](slate-2017.png)
]

@@

# 1. Insurance choice is confusing
.center[
  ![](health-affairs-2017b.png)
]

@@

.center[
  ![](health-affairs-2017.png)
]

@@

.pull-right[
  ![:scale 150%](kff-uninsured.png)
]

@@

.pull.right[
  ![:scale 50%](metal_tiers.jpg)
]

@@

.pull-right[
  ![:scale 100%](CA_Rating_Regions2.jpg)
]

@@

.center[
![:scale 85%](aca-enrollment-graph.png)
]

@@

.pull-right[
  ![](flat_comm.jpg)
]

@@

.pull-right[
  ![](perc_comm.jpg)
]

>>>>

---
title: "Insurance choice, decision assistance, and insurer steering"
subtitle: "Ian McCarthy & Evan Saltzman"
author: Carolina Region Empirical Economics Day
date: May 3, 2021 #"`r format(Sys.time(), '%d %B %Y')`"
header-includes: 
  - \usepackage{graphicx}
  - \usepackage{amsmath}
output:
#  html_document: default (toggle on for "simplified" view)
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: ["macros.js","https://platform.twitter.com/widgets.js"]
#knit: pagedown::chrome_print
---

@@

.center[
  ![](../pics/slate-2017.png)
]

@@

# 1. Insurance choice is confusing
.center[
  ![](../pics/health-affairs-2017b.png)
]

@@

.center[
  ![](../pics/health-affairs-2017.png)
]

@@

.pull-right[
  ![:scale 150%](../pics/kff-uninsured.png)
]

@@

.pull.right[
  ![:scale 50%](../pics/metal_tiers.jpg)
]

@@

.pull-right[
  ![:scale 100%](../pics/CA_Rating_Regions2.jpg)
]

@@

.center[
![:scale 85%](../pics/aca-enrollment-graph.png)
]

@@

.pull-right[
  ![](../pics/flat_comm.jpg)
]

@@

.pull-right[
  ![](../pics/perc_comm.jpg)
]
